Introduction

### 2012-10-25 dissertation/tmpsolutions.tex
srl discussion
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@412 43ef1190-90fd-4dd7-a769-d0121f02b80e

>>>>

\subsection{\SRL}

Using \SRL{} in some form, whether it is in the familiar end of
Bayesian Networks or in the relatively adventerous end of methods that
support cycles, is much more elaborate than the above strategy. I'm
quite convinced that I need to publish a paper on this topic as well,
and arguably, if I should focus at the dissertation as a whole rather
than the individual parts, it makes sense to develop this theory
first, and then derive the VoID extensions from that.

There's a whole zoo of methods in \cite{srlbook}, and at this point,
just choosing a methodology is difficult. On page~191 in this book,
there is a hypertext with typed links-example, which is very close to
the RDF model, so it is clear that there are suitable examples to work
from. Also, I have a feeling that a general methodology to learn a
Conditional Random Field from a cyclic RDF graph would be a very
significant addition to the literature, with broad applicability way
beyond the selectivity optimization use case.

However, there seems that nobody in Oslo know the CRF theory, it seems
to have been an active field of study for only about 7~years, and we don't
know anyone who works on this, so it seems to be very ambitious to
embark on.

In the acyclic case, as mentioned in section~\ref{sotasrl}, there
seems to be a pretty clear avenue for progress, and substantial
progress could be done in exploring acyclic graph patterns that are
common and how to expose them compactly.
